R tools for accessing research literature for text mining

### 2019-08-23 manuscript.tex
fix #18 link to info on where to go after getting full text

>>>>

\emph{Further processing}

From here, you'll likely want to use R packages for removing stopwords,
tokenizing, and more. The Natural Language Processing CRAN Task View
(\url{https://cloud.r-project.org/web/views/NaturalLanguageProcessing.html})
is a good place to start if you're not sure what packages to use. Some
packages worth trying in this space are
\href{https://github.com/ropensci/antiword}{antiword},
\href{https://github.com/ropensci/pdftools}{pdftools},
\href{https://github.com/ropensci/rtika}{rtika},
\href{https://github.com/ropensci/tokenizers}{tokenizers}, and
\href{https://github.com/ropensci/textreuse}{textreuse}.
